Forecasting the 2024 U.S. Presidential Election: A Poll-of-Polls Approach for Predicting the Outcome

### 2024-11-04 paper/paper.qmd
result diagram finish

library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)
library(rstanarm)
library(maps)
```

@@

```{r}
#| label: tbl-1
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Average support, Standard deviation, and the Range of polling support values for each candidate"
# Filter data for Donald Trump and Kamala Harris and calculate summary statistics
detailed_stats <- data %>%
  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
  group_by(candidate_name) %>%
  summarise(
    avg_support_pct = mean(pct, na.rm = TRUE),
    std_dev_support = sd(pct, na.rm = TRUE),
    min_support = min(pct, na.rm = TRUE),
    max_support = max(pct, na.rm = TRUE),
    num_polls = n()
  )

@@

data <- read_csv("cleaned_president_polls.csv")
important_states <- data %>%
  group_by(state, candidate_name) %>%
  summarize(avg_pct = mean(pct, na.rm = TRUE)) %>%
  arrange(state, desc(avg_pct)) %>%
  group_by(state) %>%
  mutate(margin = avg_pct - lead(avg_pct, default = 0)) %>%
  slice(1) %>%
  filter(margin < 5) # Select states with a polling margin under 5%

@@

# Load the dataset
state_support_data <- read_parquet("/Users/apple/Desktop/cleaned_president_polls.parquet")

>>>>

library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)
library(rstanarm)
library(maps)
data <- read_parquet("../data/02-analysis_data/cleaned_president_polls.parquet")
```

@@

```{r}
#| label: tbl-1
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Average support, Standard deviation, and the Range of polling support values for each candidate"
# Filter data for Donald Trump and Kamala Harris and calculate summary statistics
detailed_stats <- data %>%
  dplyr::filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
  group_by(candidate_name) %>%
  summarise(
    avg_support_pct = mean(pct, na.rm = TRUE),
    std_dev_support = sd(pct, na.rm = TRUE),
    min_support = min(pct, na.rm = TRUE),
    max_support = max(pct, na.rm = TRUE),
    num_polls = n()
  )

@@

data <- read_csv("../data/02-analysis_data/cleaned_president_polls.csv")
important_states <- data %>%
  group_by(state, candidate_name) %>%
  summarize(avg_pct = mean(pct, na.rm = TRUE)) %>%
  arrange(state, desc(avg_pct)) %>%
  group_by(state) %>%
  mutate(margin = avg_pct - lead(avg_pct, default = 0)) %>%
  slice(1) %>%
  filter(margin < 5) # Select states with a polling margin under 5%

@@

# Load the dataset
state_support_data <- read_parquet("../data/02-analysis_data/cleaned_president_polls.parquet")
